Group 5 Report

### 2022-08-01 Report/Group 5 report.Rmd
La til introduction

@@

>>>>

# Introduction

This report describes the group's approach to the problem statement and
our findings. First, the problem statement is presented, then the
brainstorming and data collection processes are elaborated, before data
description and findings are presented. Lastly, limitations and steps
forward, as well as a summary of our experience.

The project chosen for our group was Oslo Philanthropic Exchange (OPX), 
a startup working to develop solutions to assist individuals and 
organizations wanting to donate to charities and designing a socially 
responsible investment strategy.  Their main goal is to increase cash 
flow from private to charitable purposes. Therefore, the donor's trust 
in the charities’ abilities to carry out their promises is significant.

To do this, data from charities need to be collected. OPX’s current 
challenge is the data collection, which must be collected manually today
since the data is unstructured. Therefore, they wanted a way to automate 
the data collection, using web scraping.

Additionally, by creating KPIs (Key Performance Indicator), OPX can use 
them to benchmark the relationship between financial assets and emergency 
relief obligations.

The scope of the problem statement was narrowed down to the Nordic 
countries as a starting point.

It is important to solve this problem because:
Creating KPI(s) is important for the organization’s performance 
management, to influence the objective, and to foster growth
Automating the data collection will streamline the work of OPX 
and create more transparency which enhances trust in charities

@@

# Data description

# Findings

# Limitations and steps forward

# Our experience
